---
title: "A2- Gender at the Work Place"
author: "Gayatri Jadhav"
---

## Introduction

This is a dataset pertaining to gender and compensation at the workplace, modified for ease of analysis and plotting.

```{r}
#| label: setup
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
```

```{r}
workplacegender <- read_delim("../../Data/job_gender_data.csv", delim = ";")
glimpse(workplacegender)
```

```{r}
skim(workplacegender)
```

```{r}
workplacegender_clean <- workplacegender %>%
  drop_na(total_earnings_male, wage_percent_of_male)

workplacegender
```

```{r}
library(ggplot2)

# Plotting salaries and gender proportion in the workforce
ggplot(workplacegender_clean, aes(x = percent_female, y = total_earnings_male, size = total_workers)) +
  geom_point() +
  labs(x = "% of workforce reported as female", 
       y = "Median salary in the occupation", 
       size = "Total # of workers", 
       title = "Salaries and Gender Proportion in the Workforce") + scale_y_continuous(labels = scales::dollar_format()) 
#for getting the dollar sign

#I couldn't figure out a way to code the y-axis to show the median salaries as percentages instead of in scientific notation. Instead of getting the usual salary figures, I ended up with numbers like 2e+14, 4e+14, 6e+14, and 8e+14, which are super confusing. 

```

::: callout-note
-   **Target Variable:** Median salary for men in the occupation (`total_earnings_male`)

-   **Predictor Variable:** Percentage of workforce reported as female (`percent_female`)
:::

::: callout-note
The graph is a scatter plot that shows the relationship between the percentage of women in the workforce and the median salary for men in various occupations. Each dot represents a different job, and the size of the dot tells how many workers are in that job overall. The x-axis shows the percentage of female workers in that job, and the y-axis shows the median salary for male workers, with a dollar sign.

From looking at the graph, it is seen, if a job has a high percentage of female workers and men are earning less salaries, it shows some kind of inequality. And if a job has a high percentage of female workers and men are also earning good salaries, then the job pays them well regardless of their gender.
:::
