---
title: "Day2-summarizing data"
author: "Gayatri"
---

## Introduction

This is day 2 of R-class. Today, I will be summarizing data:) on Friday morning:) First, i'll be working with mdg package

```{r}
#| label: setup
library(tidyverse)
library(ggformula)
library(mosaic)
library(kableExtra)

```

## I will be looking at the new mpg dataset now

```{r}
mpg
```

```{r}
mpg %>% head(8)
```

Manufacturer is a qual, model is qual, engine displacement(displ) is a quant since the values are not discrete, they are decimal values. I can also ask the

```{r}
summary(mpg)
```

```{r}
mpg %>% dplyr::glimpse()
```

```{r}
glimpse(mpg)
```

```{r}
inspect(mpg)
```

```{r}
skimr::skim(mpg)
```

Ordinal variable is called FACTOR.

```{r}
mpg_modified <- mpg %>%
  dplyr::mutate(
    cyl = as_factor(cyl),
    fl = as_factor(fl),
    drv = as_factor(drv),
    class = as_factor(class),
    trans = as_factor(trans)
  )
glimpse(mpg_modified)
```

# Let's try this with Babynames

```{r}
library(babynames)
```

```{r}
glimpse(babynames)
```

```{r}
skimr::skim(babynames)
```

```{r}
babynames_modified <- babynames %>%
  dplyr::mutate(
    sex = as_factor(sex)
  )
glimpse(babynames_modified)
```

```{r}
babynames_modified %>% slice_sample(n=30)
```

# Analysing math Anxiety data

```{r}
math_anxiety <- read_delim(file = "../../Data/MathAnxiety.csv", delim = ";")
math_anxiety
```

```{r}
glimpse(math_anxiety)
```

```{r}
inspect(math_anxiety)
```

```{r}
math_anxiety_modified <- math_anxiety %>%
  dplyr::mutate(
    Grade = as_factor(Grade)
  )
glimpse(math_anxiety_modified)
```

```{r}
math_anxiety_modified %>%
  group_by(Grade="Primary") %>%
  summarize(average_Grade = mean(Grade), count = n())
```

```{r}
math_anxiety_modified %>%
  group_by(Gender) %>%
  summarize(average_RCMAS = mean(RCMAS), count = n())
```

```{r}
math_anxiety_modified %>%
  group_by(Gender) %>%
  summarize(average_AMAS = mean(AMAS), count = n())
```
