---
title: "Day3 - Counts"
author: "Gayatri Jadhav"
prof: "Arvind Venkatadri"
---

## Introduction

This is day 3 of R-class. Today, I will be understanding everything there is about counts. Random thought, I can count very well:) Ok, now I'll create a setup chunk first.

```{r}
#| label: setup
library(tidyverse)
library(ggformula)
library(mosaic)
library(kableExtra)
library(skimr)
```

#### First, I will be looking at the 'taxi' dataset after reading it in:

```{r}
taxi <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/modeldata/taxi.csv")
```

```{r}
glimpse(taxi)
```

```{r}
skim(taxi)
```

```{r}
inspect(taxi)
```

```{r}
## Convert `dow`, `local`, and `month` into ordered factors
taxi_modified <- taxi %>%
  mutate(
    dow = factor(dow,
      levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      labels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      ordered = TRUE
    ),
    ##
    local = factor(local,
      levels = c("no", "yes"),
      labels = c("no", "yes"),
      ordered = TRUE
    ),
    ##
    month = factor(month,
      levels = c("Jan", "Feb", "Mar", "Apr"),
      labels = c("Jan", "Feb", "Mar", "Apr"),
      ordered = TRUE
    )
  )
taxi_modified %>% glimpse()
```

```{r}
## Set graph theme
theme_set(new = theme_classic())
##theme_custom doesn't work for me:(


#the tilda symbol below '~' signifies that tip is on the x-axis. So basically tilda(~) to the left of anything means that variable is on the x-axis. So here, local is also on the x-axis, but as color.
#color = ~local only shows the outline, whereas, fill is used to color it inside as well
#two variable are used here, tip and local. local is married to color.
gf_bar(~tip, data = taxi_modified, fill = ~local,) %>%
  gf_labs(title = "Plot 1A: Counts of Tips")


    
```

```{r}

## Set graph theme
theme_set(new = theme_classic())
##

#position ="stack" is default
gf_bar(~tip, data = taxi_modified, fill = ~local, position="dodge",) %>%
  gf_labs(title = "Plot 1A: Counts of Tips")
 
```

```{r}
## Set graph theme
theme_set(new = theme_classic())
##

#Question-Do non-local people tip more than local people?

## Showing "per capita" percentages
## Better labelling of Y-axis
taxi_modified %>%
  gf_bar(~local,
    fill = ~tip,
    position = "fill"
  ) %>%
  gf_labs(
    title = "Plot 2D: Filled Bar Chart",
    subtitle = "Shows Per group differences in Proportions!"
  )
```

```{r}
## Set graph theme
theme_set(new = theme_classic())
#

#Question-which company has the most non-tippers?
## Showing "per capita" percentages
## Better labelling of Y-axis
taxi_modified %>%
  gf_bar(~company, fill = ~tip, position = "fill") %>%
  gf_labs(
    title = "Plot 2D: Filled Bar Chart",
    subtitle = "Shows Per group differences in Proportions!"
  ) %>%
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
## Set graph theme
theme_set(new = theme_classic())

#5pm is the busiest hour and 3pm the least.
##
gf_bar(~hour, fill = ~tip, data = taxi_modified) %>%
  gf_labs(title = "Plot B: Counts of Tips by Hour")
```

```{r}
## Set graph theme
theme_set(new = theme_classic())

#5pm is the busiest hour and 3pm the least.
##
gf_bar(~hour, fill = ~tip, data = taxi_modified, position = "fill") %>%
  gf_labs(title = "Plot B: Counts of Tips by Hour")
```

```{r}
##
## This may be too busy a graph...
gf_bar(~ dow | hour, fill = ~tip, data = taxi_modified, position = "fill") %>%
  gf_labs(
    title = "Plot F: Counts of Tips by Hour and Day of Week",
    subtitle = "Is this plot arrangement easy to grasp?"
  )
```

```{r}
##
## This may be too busy a graph...
gf_bar(~hour, fill = ~tip, data = taxi_modified, position = "fill") %>%
  gf_labs(
    title = "Plot F: Counts of Tips by Hour and Day of Week",
    subtitle = "Is this plot arrangement easy to grasp?"
  )
```

#### Dataset -2 - HELPrct

I dropped my phone just now, and I think the display might have been broken. Wow, I might go bankrupt fixing it:) So i will take a break now.

```{r}
data(HELPrct)
inspect(HELPrct)
```

### *My Turn - A1 (*Calm Mode Data Analysis)\* Datset 3 -\* I will be analysing 'Stigler' Dataset :

#### Purpose: To Calculate An Optimal Diet

This is a dataset that contains nutritional values of household commodities. The dataset was used in the "stigler"-problem where ones tries to figure out how to minimize the costs of food while still getting enough nutrients.

```{r read stig}
stig <- read.csv(file = "../../Data/stigler.csv")
```

```{r}
names(stig)
```

```{r}
head(stig)

```

```{r}
tail(stig)
```

```{r}
summary(stig)
```

## Graph 1

### Quantitative Analysis

```{r}
ggplot(data = stig, (aes(x = calcium_g, fill = "pink"))) + geom_bar(color = "black") + ggtitle("A bar geom with cut")
```

## Graph 2

### Quantity Vs Quantity

```{r}
ggplot(data = stig, aes(x = price_cents, y = niacin_mg)) + geom_jitter(color = "magenta") + geom_smooth(method = lm) + ggtitle("A point geom with jittered data points")
```

## Graph 3

### Quantity Vs Quantity

```{r}
ggplot(data = stig, aes(x = price_cents, y = calories)) + geom_line(color = "red") + ggtitle(label = "A line graph")
```

\# **End of A1**
