---
title: "A2- School Scores"
author: "Gayatri Jadhav"
---

## Introduction

This dataset pertains to scores obtained by students in diverse subjects. Family Income is also part of this dataset.

The research probably asked high school students from different states about things like their family income, grades, and gender to see how these affect their math and verbal test scores.

```{r}
#| label: setup
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
library(GGally)
library(janitor)
```

```{r}
#Reading in the dataset
schoolscores <- read_delim("../../Data/school-scores-data.csv", delim = ",")

glimpse(schoolscores)
```

```{r}
class(schoolscores) 
#checked the class since i was getting an Error in the next code chunk: A data frame is not a valid object for this function. I used the oldest trick in the book and restarted R for it to work.
```

```{r}

#Hint: Use the janitor package here to clean up the variable names. Try to use the big_camel case name format for variables.(Hint given on the website)

# Clean the variable names
schoolscores <- schoolscores %>%
  clean_names(case = "big_camel")


```

```         
Error in clean_names(., case = "big_camel") :    could not find function "clean_names"
```

After this error, I am installing the Janitor package.\
Maybe, I'm too sleepy, it took me literally 30 mins to figure that the limiter for this dataset was "," and not ";"

## Data Dictionary-

::: callout-note
## Quantitative Variables

-   **Year**: Represents the year of the data collection (type: \<dbl\>).

-   **TotalMath**: Total math scores (type: \<dbl\>).

-   **TotalTestTakers**: Number of students taking the test (type: \<dbl\>).

-   **TotalVerbal**: Total verbal scores (type: \<dbl\>).

-   **AcademicSubjectsArtsMusicAverageGpa**: Average GPA in Arts/Music (type: \<dbl\>).

-   **AcademicSubjectsEnglishAverageGpa**: Average GPA in English (type: \<dbl\>).

-   **AcademicSubjectsForeignLanguagesAverageGpa**: Average GPA in Foreign Languages (type: \<dbl\>).

-   **AcademicSubjectsMathematicsAverageGpa**: Average GPA in Mathematics (type: \<dbl\>).

-   **AcademicSubjectsNaturalSciencesAverageGpa**: Average GPA in Natural Sciences (type: \<dbl\>).

-   **AcademicSubjectsSocialSciencesHistoryAverageGpa**: Average GPA in Social Sciences/History (type: \<dbl\>).

-   **FamilyIncomeBetween20_40KMath**: Math scores for families with income between 20K and 40K (type: \<dbl\>).

-   **FamilyIncomeBetween20_40KVerbal**: Verbal scores for families with income between 20K and 40K (type: \<dbl\>).

-   **FamilyIncomeBetween40_60KMath**: Math scores for families with income between 40K and 60K (type: \<dbl\>).

-   **FamilyIncomeBetween40_60KVerbal**: Verbal scores for families with income between 40K and 60K (type: \<dbl\>).

-   **FamilyIncomeBetween60_80KMath**: Math scores for families with income between 60K and 80K (type: \<dbl\>).

-   **FamilyIncomeBetween60_80KVerbal**: Verbal scores for families with income between 60K and 80K (type: \<dbl\>).

-   **FamilyIncomeMoreThan100KMath**: Math scores for families with income over 100K (type: \<dbl\>).

-   **FamilyIncomeMoreThan100KVerbal**: Verbal scores for families with income over 100K (type: \<dbl\>).

-   **GenderFemaleMath**: Math scores for female students (type: \<dbl\>).

-   **GenderFemaleVerbal**: Verbal scores for female students (type: \<dbl\>).

-   **GenderMaleMath**: Math scores for male students (type: \<dbl\>).

-   **GenderMaleVerbal**: Verbal scores for male students (type: \<dbl\>).

-   **ScoreRangesBetween200To300MathFemales**: Female scores in the 200-300 range (type: \<dbl\>).

-   **ScoreRangesBetween200To300MathMales**: Male scores in the 200-300 range (type: \<dbl\>).

-   **ScoreRangesBetween300To400MathFemales**: Female scores in the 300-400 range (type: \<dbl\>).

-   **ScoreRangesBetween300To400MathMales**: Male scores in the 300-400 range (type: \<dbl\>).

-   **ScoreRangesBetween400To500MathFemales**: Female scores in the 400-500 range (type: \<dbl\>).

-   **ScoreRangesBetween400To500MathMales**: Male scores in the 400-500 range (type: \<dbl\>).

-   **ScoreRangesBetween500To600MathFemales**: Female scores in the 500-600 range (type: \<dbl\>).

-   **ScoreRangesBetween500To600MathMales**: Male scores in the 500-600 range (type: \<dbl\>).

-   **ScoreRangesBetween600To700MathFemales**: Female scores in the 600-700 range (type: \<dbl\>).

-   **ScoreRangesBetween600To700MathMales**: Male scores in the 600-700 range (type: \<dbl\>).

-   **ScoreRangesBetween700To800MathFemales**: Female scores in the 700-800 range (type: \<dbl\>).

-   **ScoreRangesBetween700To800MathMales**: Male scores in the 700-800 range (type: \<dbl\>).
:::

::: callout-note
## Qualitative Variables

-   **StateCode**: Code representing the state (type: \<chr\>).

-   **StateName**: Name of the state (type: \<chr\>).

-   **Gender**: Gender classification of students
:::

::: callout-note
#### Observations

-   **Rows and columns**: The dataset consists of 577 rows and 99 columns
:::

## Replicating the plot

```{r}
# Set graph theme
theme_set(new = theme_classic())

# Create the ggpairs plot
GGally::ggpairs(
  schoolscores %>% drop_na(),
  # Select Quant variables(target variables) only for now
  columns = c(
    "AcademicSubjectsArtsMusicAverageGpa", "AcademicSubjectsEnglishAverageGpa", 
    "AcademicSubjectsForeignLanguagesAverageGpa", 
    "AcademicSubjectsMathematicsAverageGpa", 
    "AcademicSubjectsNaturalSciencesAverageGpa", 
    "AcademicSubjectsSocialSciencesHistoryAverageGpa"
  ),
  switch = "both",
  # axis labels in more traditional locations (left and bottom)
  progress = FALSE,
  # no compute progress messages needed
  
  # Choose the diagonal graphs (always single variable)
  diag = list(continuous = "barDiag"),  # Choosing histogram, not density
  # Choose lower triangle graphs, two-variable graphs
  lower = list(continuous = wrap("smooth", alpha = 0.3, se = FALSE))
) + 
  ggtitle("Academic Scores in Different Subjects")

```

::: callout-note
The above plot shows correlations between average GPAs in various subjects. For example, students who perform well in English Subject often also achieve high GPAs in Social Sciences, indicating a possible connection between success in language subjects and success in subjects that involve thinking and analysis.

If the target variable is `AcademicSubjectsMathematicsAverageGpa`, then the GPAs in subjects like English, Arts & Music, Foreign Languages, Natural Sciences, and Social Sciences would be your predictor variables.

**Questions to answer-**

-   Do students who get good grades in one subject also do well in other subjects?

-   Are some subjects more closely connected in terms of grades?

-   Does doing well in creative subjects like art and music mean you're likely to do well in academic subjects too?
:::
