---
title: "A3 - Tips Dataset"
author: "Gayatri Jadhav"
prof: "Arvind Venkatadri"
---

## Introduction

This dataset looks at **tips** left by restaurant customers and includes details like their **gender** and whether they prefer **Veg** or **Non-Veg** food. It helps see if there are any patterns, like whether people who eat certain types of food tip more or if certain groups tend to give bigger tips.

```{r}
#| label: setup
library(tidyverse) # Data Processing in R
library(mosaic) # Our workhorse for stats, sampling
library(ggformula)
library(skimr)
library(crosstable)
```

```{r}
tip <- read_csv("../../Data/tip.csv")

glimpse(tip)
```

```{r}
# Crosstabulating the Tip variable against Preferance (categorical variable) to summarize the relationship
# This helped me understand how tips are distributed across the two preferences (Veg/Non-veg)

tip %>% 
  crosstable(Tip ~ Preferance) %>% 
  as_flextable()

```

```{r}
# Mutating by converting Gender and Preferance into factors

tips_modified <- tip %>%
  dplyr::mutate(
  Gender = as_factor(Gender),
  Preferance = as_factor(Preferance)
  )
glimpse(tips_modified)


```

```{r}
# Creating a histogram to see the distribution of Tips by Preferance
tips_modified %>%
  gf_histogram(~Tip|Preferance, fill = ~Preferance,position= "dodge" ,data = tips_modified) 
```

```{r}
Veg <- tips_modified %>% 
  filter(Preferance == "Veg") %>% 
  select(Tip)

Nonveg <- tips_modified %>% 
  filter(Preferance == "Non-veg") %>% 
  select(Tip)

shapiro.test(Veg$Tip) # Performing the Shapiro-Wilk test for normality on the "Veg" group's Tip values

shapiro.test(Nonveg$Tip)# Performing the Shapiro-Wilk test for normality on the "Non-veg" group's Tip values

```

::: callout-note
The p-values are extremely small, indicating that neither the Veg nor the Non-veg Tip data is normally distributed.
:::

```{r}
mosaic::t_test( Tip ~ Preferance, data = tips_modified ) %>% 

  broom::tidy() 
```

::: callout-note
Since neither the Veg nor Non-veg Tip data is normally distributed, using a t-test wouldn't be the right choice. Instead, it's better to use the **Wilcoxon test**, which is a non-parametric method that's ideal for comparing the medians when the data isn’t normally distributed.
:::

Splitting the dataset by Preferance into Veg and Nonveg groups-

```{r}

#Selecting only the Tip column for further testing
tips_modified %>% 
  filter(Preferance == "Veg") %>% 
  select(Tip) -> Veg

# Checking the "Veg" group Tip values
Veg


```

```{r}
#Extracting the Tip values for the "Non-veg" group
tips_modified %>% 
  filter(Preferance == "Non-veg") %>% 
  select(Tip) -> Nonveg

# Checking the "Non-veg" group Tip values
Nonveg 
```

```{r}
wilcox.test(Tip ~ Preferance , data = tips_modified) %>% 
  broom::tidy()
```

::: callout-note
The Wilcoxon test gave a result of 437 for the statistic and a **p-value of 0.83**. This high p-value means there’s no significant difference between the tips left by the Veg and Non-veg groups. IBoth groups leave about the same amount in tips.
:::

```{r}
obs_diff_tip <- diffmean( Tip ~ Preferance, data = tips_modified) 
obs_diff_tip
```

::: callout-note
The **diffmean** result is **-2.33**, which means that, on average, the Non-veg group left 2.33 less in tips than the Veg group. But because the Wilcoxon test has not showed any significant difference, this small difference doesn’t actually matter much.
:::

```{r}
# Generating a null distribution for the difference in means through permutation testing (5000 permutations)
null_dist_tip <- 
  do(4999) * diffmean(data = tips_modified, Tip ~ shuffle(Preferance))
null_dist_tip

#Everytime I run it, the values are different since the data is shuffled.

```

```{r}
# Set graph theme
theme_set(new = theme_classic())
#
gf_histogram(data = null_dist_tip, ~ diffmean, bins = 25) %>%
  gf_vline(xintercept = obs_diff_tip, 
           colour = "red", linewidth = 1,
           title = "Null Distribution by Permutation", 
           subtitle = "Histogram") %>% 
  gf_labs(x = "Difference in Means")
###
gf_ecdf(data = null_dist_tip, ~ diffmean, 
        linewidth = 1) %>%
  gf_vline(xintercept = obs_diff_tip, 
           colour = "red", linewidth = 1,
           title = "Null Distribution by Permutation", 
           subtitle = "Cumulative Density") %>% 
  gf_labs(x = "Difference in Means")
```

::: callout-note
Inference:-

-   The **histogram** shows the differences between the two groups (Veg and Non-veg) when the data is shuffled randomly. The red line shows the actual difference that was observed (-2.33).

-   Since the red line falls in the middle of the random results,so the difference is not unusual- it could just be due to random chance.

-   The **cumulative plot** (the second graph) backs this up. It shows that the observed difference is well within what I’d expect if there was no real difference.

**Conclusion**: There's no strong evidence that the difference in tips between Veg and Non-veg preferences is meaningful, it could easily be due to chance. I initially thought the tips dataset might be useless because of the lack of significant differences between the groups. However, during class, i realised that even with no significant results, the data can still provide valuable insights into patterns and trends in tipping behavior. So, it's definitely not useless!
:::

sample data\
mean\
shapiro\
t-test\
if necessary winc

<https://av-quarto.netlify.app/content/courses/analytics/inference/modules/110-twomeans/#observed-and-test-statistic>
