---
title: "Day-6"
author: "Gayatri Jadhav"
---

population - parameters

sample - statistics

sample mean and population mean

sample mean is equally likely to be on either side. (it is fair)

any mean can be positive or negative

whereas, sd(standard deviation0 can never be negative

the mean of the sample mean is the population mean

Bell curve

Should the conference interval be big or smaller? (answer is smaller) So we are sure -95 % , so we have to trust the sample mean

The lady who drank tea story - if those same tea-cups were reshuffled and given

rng - random number generation poisson distribution

Statistical Inference ---\> Samples, Populations, Statistics and Inference

```{r}
library(tidyverse)
library(mosaic)
library(ggformula)
library(infer)
library(broom) # Clean test results in tibble form
library(resampledata) # Datasets from Chihara and Hesterberg's book
library(openintro) # More datasets
```

```{r}

set.seed(40)  # for repldata:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAcElEQVR4Xu3OwQmAQAxE0bClWYCW5N06tM6V2YPg5CjoF/JhLoHAi6iqn9eOefUbqrYvHY0cQDLyAlKRNyARmYA0ZMLRkAlGQyaU72tkAtlim7r/vJqDUDjlKBROOQyFU2icQuMUGqfQuBEaV1XPOwEx96nYACK8+wAAAABJRU5ErkJggg==ication
# Data as individual vectors ( for t.tests etc)
y <- rnorm(50, mean = 2, sd = 2)

# And as tibble too
mydata <- tibble(y = y)
mydata

```

```{r}
# Set graph theme
theme_set(new = theme_classic())
#
mydata %>%
    gf_density(~y) %>%
    gf_fitdistr(dist = "dnorm") %>%
    gf_labs(title = "Densities of Original Data Variables", subtitle = "Compared with Normal Density")
```

```{r}

# t-test
t1 <- mosaic::t_test(
          y, # Name of variable
          mu = 0, # belief of population mean
          alternative = "two.sided") %>% # Check both sides
  
  broom::tidy() # Make results presentable, and plottable!!
t1
```


#| eval: false
Use this if you don't want the chunk to run