---
title: "Day 5 - Groups, Change"
author: "Gayatri Jadhav"
---

## Introduction

This is day 5 of R-class. Today, I will be exploring Groups. I will understand how boxplots work.

```{r}
#| label: setup
library(tidyverse)
library(ggformula)
library(mosaic)
library(kableExtra)
library(skimr)
```

```{r}
wages <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/stevedata/gss_wages.csv")

glimpse(wages)
```

```{r}
skim(wages)
```

```{r}
inspect(wages)
```

```{r}
wages_clean <-
  wages %>%
  tidyr::drop_na(realrinc) 

```

```{r}
# Set graph theme
theme_set(new = theme_classic())
#
wages_clean %>%
  gf_boxplot(realrinc ~ "Income") %>% # Dummy X-axis "variable"
  gf_labs(
    title = "Plot 1A: Income has a skewed distribution",
    subtitle = "Many outliers on the high side"
  )
```

```{r}
# Set graph theme
theme_set(new = theme_classic())
#
wages_clean %>%
  gf_boxplot(gender ~realrinc ) %>%
  gf_labs(title = "Plot 2A: Income by Gender")

```

```{r}
# Set graph theme
theme_set(new = theme_classic())
##
wages_clean %>%
  gf_boxplot(gender ~ log10(realrinc)) %>%
  gf_labs(title = "Plot 2B: Log(Income) by Gender")
```

```{r}
# Set graph theme
theme_set(new = theme_classic())
#
wages_clean %>%
  gf_boxplot(wrkstat ~realrinc ) %>%
  gf_labs(title = "Plot 2A: Income by Work Status")
```

```{r}
# Set graph theme
theme_set(new = theme_classic())
##
wages_clean %>%
  gf_boxplot(educcat ~ log10(realrinc)) %>%
  gf_labs(title = "Plot 2B: Log(Income) by Gender")
```

```{r}
wages_clean <-
  wages %>%
  tidyr::drop_na(educcat) 

glimpse(wages_clean)
```

```{r}
# Set graph theme
theme_set(new = theme_classic())
#
wages_clean %>%
  gf_boxplot(educcat ~realrinc ) %>%
  gf_labs(title = "Plot 2A: Income by Work Status")
```

**Why use log income instead of income?(google search)**

When dealing with income level or economic value, the numbers are generally large. **The log has the effect of de-scaling effect of the large number for ease of handling**. After the calculation or modeling is complete, the final result can be converted back to its original scale.

Quant vs quant

```{r}

library(GGally) # Corr plots
library(corrplot) # More corrplots
library(ggExtra) # Making Combination Plots

# devtools::install_github("rpruim/Lock5withR")
library(Lock5withR) # Datasets
library(palmerpenguins) # A famous dataset

library(easystats) # Easy Statistical Analysis and Charts
library(correlation) # Different Types of Correlations
# From the easystats collection of packages
```

```{r}
HollywoodMovies2011 -> movies

movies_quant <- movies %>%
  drop_na() %>%
  select(where(is.numeric))
glimpse(movies_quant)
```

```{r}
# Set graph theme
theme_set(new = theme_classic())

movies %>%
  gf_point(DomesticGross ~ WorldGross) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movie Gross Earnings: Domestics vs World"
  )
```

```{r}
# Set graph theme
theme_set(new = theme_classic())
movies %>%
  gf_point(Profitability ~ OpeningWeekend) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movies: Does Opening Week Earnings indicate Profitability?"
  )
```

```{r}
# Set graph theme
theme_set(new = theme_classic())
movies %>%
  gf_point(Profitability ~ AudienceScore) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Does the Audience Score affect the Profitability?"
    
    #No, it is not affecting the profitability as the slope is 0.
  )
```

```{r}
# Set graph theme
theme_set(new = theme_classic())

##Rotten tomatoes is website that rates movies
movies %>%
  gf_point(RottenTomatoes ~ AudienceScore) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movie Ratings: Tomatoes vs Audience"
  )
```

```{r}
# Set graph theme
theme_set(new = theme_classic())

movies %>%
  drop_na() %>%
  gf_point(RottenTomatoes ~ AudienceScore,
    color = ~Genre
  ) %>%
  gf_lm() %>%
  gf_labs(
    title = "Scatter Plot",
    subtitle = "Movie Ratings: Trends by Genre"
  )
```

#Best fit line

```{r}
# Set graph theme
theme_set(new = theme_classic())

# names(movies_quant)

GGally::ggpairs(
  movies %>% drop_na(),
  # Select Quant variables only for now
  columns = c(
    "RottenTomatoes", "AudienceScore", "DomesticGross", "ForeignGross" ,"Budget", "Profitability"
  ),
  switch = "both",
  # axis labels in more traditional locations(left and bottom)

  progress = FALSE,
  # no compute progress messages needed

  # Choose the diagonal graphs (always single variable! Think!)
  diag = list(continuous = "barDiag"),
  # choosing histogram,not density

  # Choose lower triangle graphs, two-variable graphs
  lower = list(continuous = wrap("smooth", alpha = 0.3, se = FALSE)),
  title = "Movies Data Correlations Plot #1"
)
```

#A2- what can be the target variables, what might have been the research behind this dataset, make graphs and ask what question does this graph answer. It is okay if i wanted to ask smtg but it reveals smtg else. Define data dictionary.Make 3 files. A2-A (index.qmd), A2-B(index.qmd), A2-C (index.qmd).Choose any 3 datasets from the link uploaded.
